---
title: "Descriptive Statistics"
author: "Rodolfo Pelinson"
date: "13/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These are just means and variability of the environmental predictors used both in the EMS and Variation partitioning analyses.

First we have to load the separated data matrices we need. The data matrices are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
library(AtlanticForestMetacommunity)
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(AtlanticForestMetacommunity)
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
```


### Number of Species

#### Broad Extent
```{r}
ncol(Broad_pa_orig)
```
\   
\  

#### Intermediate Extent
DRF
```{r}
ncol(DRF_pa_orig)
```
\  
\  

SSF
```{r}
ncol(SSF_pa_orig)

```
\  
\  

Species in commom SSF-DRF
```{r}
sp_comm <- na.omit(match(colnames(DRF_pa_orig), colnames(SSF_pa_orig)))
length(sp_comm)
colnames(SSF_pa_orig)[sp_comm]
```
\  
\  
\  
\  


#### Small Extent

DRF - Ubatuba
```{r}
ncol(UBA_pa_orig)
```
\  
\  

DRF - Bertioga
```{r}
ncol(BER_pa_orig)
```
\  
\  

DRF - Itanhaém
```{r}
ncol(ITA_pa_orig)
```
\  
\  

Species in commom UBA-BER
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  

Species in commom UBA-ITA
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(ITA_pa_orig)))
length(sp_comm)
colnames(ITA_pa_orig)[sp_comm]
```
\  
\  

Species in commom ITA-BER
```{r}
sp_comm <- na.omit(match(colnames(ITA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  
\ 
\  


SSF - Santa Fé do Sul
```{r}
ncol(ST_pa_orig)

```
\  
\  

SSF - Icém
```{r}
ncol(IC_pa_orig)
```
\  
\  

SSF - Nova Itapirema
```{r}
ncol(NI_pa_orig)
```
\  
\  

SSF - Morro do Diabo
```{r}
ncol(MD_pa_orig)
```
\  
\  

SSF - Jataí
```{r}
ncol(JA_pa_orig)
```
\  
\  

Species in commom ST-IC
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(IC_pa_orig)))
length(sp_comm)
colnames(IC_pa_orig)[sp_comm]
```
\  
\  

Species in commom ST-NI
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  


Species in commom ST-MD
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


Species in commom ST-JA
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

Species in commom IC-NI
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  

Species in commom IC-MD
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


Species in commom IC-JA
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  



Species in commom NI-MD
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  

Species in commom NI-MD
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

Species in commom JA-MD
```{r}
sp_comm <- na.omit(match(colnames(MD_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  
\  
\  
\  
\  
\  
\  



### Means of continuous variables
Intermediate Extent
```{r}
data.frame(DRF_mean = apply(DRF_clim, 2, mean), SSF_mean = apply(SSF_clim, 2, mean))
data.frame(DRF_mean = apply(DRF_env[,3:5], 2, mean), SSF_mean = apply(SSF_env[,3:5], 2, mean))
```
\  
\  


Small Extent
```{r}
data.frame(UBA_mean = apply(UBA_env[,3:5], 2, mean),
           BER_mean = apply(BER_env[,3:5], 2, mean),
           ITA_mean = apply(ITA_env[,3:5], 2, mean),
           ST_mean = apply(ST_env[,3:5], 2, mean),
           IC_mean = apply(IC_env[,3:5], 2, mean),
           NI_mean = apply(NI_env[,3:5], 2, mean),
           MD_mean = apply(MD_env[,3:5], 2, mean),
           JA_mean = apply(JA_env[,3:5], 2, mean))
```
\  
\  
\  
\  


### Coefficient of Variation of continuous variables

Intermediate Extent
```{r}
data.frame(DRF_cv = apply(DRF_clim, 2, cv), SSF_cv = apply(SSF_clim, 2, cv))
data.frame(DRF_cv = apply(DRF_env[,3:5], 2, cv), SSF_cv = apply(SSF_env[,3:5], 2, cv))
```
\  
\  


Small Extent
```{r}
data.frame(UBA_cv = apply(UBA_env[,3:5], 2, cv),
           BER_cv = apply(BER_env[,3:5], 2, cv),
           ITA_cv = apply(ITA_env[,3:5], 2, cv),
           ST_cv = apply(ST_env[,3:5], 2, cv),
           IC_cv = apply(IC_env[,3:5], 2, cv),
           NI_cv = apply(NI_env[,3:5], 2, cv),
           MD_cv = apply(MD_env[,3:5], 2, cv),
           JA_cv = apply(JA_env[,3:5], 2, cv))
```

