---
title: "Descriptive Statistics"
author: "Rodolfo Pelinson"
date: "13/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here you can find the number and identity of species at all spatial extents, localities and ecoregions. We also show here which species are shared between ecoregions and localities.

We also show maximum, minimum, and mean values of each environmental variable considered in all analyses at all spatial extents, localities and ecoregions.
\ 
\ 
\ 

First we need preparare all data matrices from the main dataset. These are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
library(AtlanticForestMetacommunity)
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(AtlanticForestMetacommunity)
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
```


## Number of Species

### Large Extent
```{r}
ncol(Broad_pa_orig)
```
\   
\  

### Intermediate Extent

#### DRF
```{r}
ncol(DRF_pa_orig)
```
\  

#### SSF
```{r}
ncol(SSF_pa_orig)

```
\  
\ 


### Small Extent

#### SSF - Santa Fé do Sul
```{r}
ncol(ST_pa_orig)

```
\  

#### SSF - Icém
```{r}
ncol(IC_pa_orig)
```
\  

#### SSF - Nova Itapirema
```{r}
ncol(NI_pa_orig)
```
\  

#### SSF - Morro do Diabo
```{r}
ncol(MD_pa_orig)
```
\  

#### SSF - Jataí
```{r}
ncol(JA_pa_orig)
```
\  

#### DRF - Ubatuba
```{r}
ncol(UBA_pa_orig)
```
\  

#### DRF - Bertioga
```{r}
ncol(BER_pa_orig)
```
\  

#### DRF - Itanhaém
```{r}
ncol(ITA_pa_orig)
```
\  
\ 
\ 
\ 
\ 


## Species Shared

### Intermediate Extent

```{r}
sp_comm <- na.omit(match(colnames(DRF_pa_orig), colnames(SSF_pa_orig)))
length(sp_comm)
colnames(SSF_pa_orig)[sp_comm]
```
\  
\  


### Small Extent

#### Santa Fé do Sul - Icém
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(IC_pa_orig)))
length(sp_comm)
colnames(IC_pa_orig)[sp_comm]
```
\  
\  

#### Santa Fé do Sul - Nova Itapirema
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  


#### Santa Fé do Sul - Morro do Diabo
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


#### Santa Fé do Sul - Jataí
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

#### Icém - Nova Itapirema
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  

#### Icém - Morro do Diabo
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


#### Icém - Jataí
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

#### Nova Itapirema - Morro do Diabo
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  

#### Nova Itapirema - Jataí
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

#### Morro do Diabo - Jataí
```{r}
sp_comm <- na.omit(match(colnames(MD_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

#### Ubatuba - Bertioga
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  

#### Ubatuba - Itanhaém
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(ITA_pa_orig)))
length(sp_comm)
colnames(ITA_pa_orig)[sp_comm]
```
\  
\  

#### Itanhaém - Bertioga
```{r}
sp_comm <- na.omit(match(colnames(ITA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  
\  
\  
\  



## Means, maximum and minimum of predictor variables
\  

### Intermediate Extent

#### DRF
```{r}
data.frame(DRF_min = apply(DRF_clim, 2, min), DRF_mean = apply(DRF_clim, 2, mean), DRF_max = apply(DRF_clim, 2, max))
data.frame(DRF_min = apply(DRF_env, 2, min), DRF_mean = apply(DRF_env, 2, mean), DRF_max = apply(DRF_env, 2, max))
```
\  

#### 
```{r}
data.frame(SSF_min = apply(SSF_clim, 2, min), SSF_mean = apply(SSF_clim, 2, mean), SSF_max = apply(SSF_clim, 2, max))
data.frame(SSF_min = apply(SSF_env, 2, min), SSF_mean = apply(SSF_env, 2, mean), SSF_max = apply(SSF_env, 2, max))

```


\  
\  


### Small Extent

#### Santa Fé do Sul
```{r}
data.frame(ST_min = apply(ST_env, 2, min),
  ST_mean = apply(ST_env, 2, mean),
  ST_max = apply(ST_env, 2, max))
```
\  

#### Icém
```{r}
data.frame(IC_min = apply(IC_env, 2, min),
  IC_mean = apply(IC_env, 2, mean),
  IC_max = apply(IC_env, 2, max))
```
\  

#### Nova Itapirema
```{r}
data.frame(NI_min = apply(NI_env, 2, min),
  NI_mean = apply(NI_env, 2, mean),
  NI_max = apply(NI_env, 2, max))
```
\  

#### Morro do Diabo
```{r}
data.frame(MD_min = apply(MD_env, 2, min),
  MD_mean = apply(MD_env, 2, mean),
  MD_max = apply(MD_env, 2, max))
```
\  

#### Jataí
```{r}
data.frame(JA_min = apply(JA_env, 2, min),
  JA_mean = apply(JA_env, 2, mean),
  JA_max = apply(JA_env, 2, max))
```
\ 

#### Ubatuba
```{r}
data.frame(UBA_min = apply(UBA_env, 2, min),
  UBA_mean = apply(UBA_env, 2, mean),
  UBA_max = apply(UBA_env, 2, max))
```
\  

#### Bertioga
```{r}
data.frame(BER_min = apply(BER_env, 2, min),
  BER_mean = apply(BER_env, 2, mean),
  BER_max = apply(BER_env, 2, max))
```
\  

#### Itanhaém
```{r}
data.frame(ITA_min = apply(ITA_env, 2, min),
  ITA_mean = apply(ITA_env, 2, mean),
  ITA_max = apply(ITA_env, 2, max))
```
\  
\  
\  
\  
\  



## Coefficient of Variation of predictor variables

### Intermediate Extent
```{r}
Int_Clim_cv <- data.frame(DRF_cv = apply(DRF_clim, 2, coef_var), SSF_cv = apply(SSF_clim, 2, coef_var))
Int_Env_cv <- data.frame(DRF_cv = apply(DRF_env, 2, coef_var), SSF_cv = apply(SSF_env, 2, coef_var))

Int_Clim_cv
Int_Env_cv

apply(Int_Clim_cv, 2, mean)
apply(Int_Env_cv, 2, mean)
```
\  
\  


### Small Extent
```{r}
Sm_Env_cv <- data.frame(UBA_cv = apply(UBA_env, 2, coef_var),
           BER_cv = apply(BER_env, 2, coef_var),
           ITA_cv = apply(ITA_env, 2, coef_var),
           ST_cv = apply(ST_env, 2, coef_var),
           IC_cv = apply(IC_env, 2, coef_var),
           NI_cv = apply(NI_env, 2, coef_var),
           MD_cv = apply(MD_env, 2, coef_var),
           JA_cv = apply(JA_env, 2, coef_var))

Sm_Env_cv
apply(Sm_Env_cv, 2, mean)
```

