---
title: "Descriptive Statistics"
author: "Rodolfo Pelinson"
date: "13/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These are just means and variability of the environmental predictors used both in the EMS and Variation partitioning analyses.

First we have to load the separated data matrices we need. The data matrices are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
library(AtlanticForestMetacommunity)
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(AtlanticForestMetacommunity)
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
```


### Number of Species

#### Broad Extent
```{r}
ncol(Broad_pa_orig)
```
\   
\  

#### Intermediate Extent
DRF
```{r}
ncol(DRF_pa_orig)
```
\  
\  

SSF
```{r}
ncol(SSF_pa_orig)

```
\  
\  

Species in commom SSF-DRF
```{r}
sp_comm <- na.omit(match(colnames(DRF_pa_orig), colnames(SSF_pa_orig)))
length(sp_comm)
colnames(SSF_pa_orig)[sp_comm]
```
\  
\  
\  
\  


#### Small Extent

DRF - Ubatuba
```{r}
ncol(UBA_pa_orig)
```
\  
\  

DRF - Bertioga
```{r}
ncol(BER_pa_orig)
```
\  
\  

DRF - Itanhaém
```{r}
ncol(ITA_pa_orig)
```
\  
\  

Species in commom UBA-BER
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  

Species in commom UBA-ITA
```{r}
sp_comm <- na.omit(match(colnames(UBA_pa_orig), colnames(ITA_pa_orig)))
length(sp_comm)
colnames(ITA_pa_orig)[sp_comm]
```
\  
\  

Species in commom ITA-BER
```{r}
sp_comm <- na.omit(match(colnames(ITA_pa_orig), colnames(BER_pa_orig)))
length(sp_comm)
colnames(BER_pa_orig)[sp_comm]
```
\  
\  
\ 
\  


SSF - Santa Fé do Sul
```{r}
ncol(ST_pa_orig)

```
\  
\  

SSF - Icém
```{r}
ncol(IC_pa_orig)
```
\  
\  

SSF - Nova Itapirema
```{r}
ncol(NI_pa_orig)
```
\  
\  

SSF - Morro do Diabo
```{r}
ncol(MD_pa_orig)
```
\  
\  

SSF - Jataí
```{r}
ncol(JA_pa_orig)
```
\  
\  

Species in commom ST-IC
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(IC_pa_orig)))
length(sp_comm)
colnames(IC_pa_orig)[sp_comm]
```
\  
\  

Species in commom ST-NI
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  


Species in commom ST-MD
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


Species in commom ST-JA
```{r}
sp_comm <- na.omit(match(colnames(ST_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

Species in commom IC-NI
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(NI_pa_orig)))
length(sp_comm)
colnames(NI_pa_orig)[sp_comm]
```
\  
\  

Species in commom IC-MD
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  


Species in commom IC-JA
```{r}
sp_comm <- na.omit(match(colnames(IC_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  



Species in commom NI-MD
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(MD_pa_orig)))
length(sp_comm)
colnames(MD_pa_orig)[sp_comm]
```
\  
\  

Species in commom NI-MD
```{r}
sp_comm <- na.omit(match(colnames(NI_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  

Species in commom JA-MD
```{r}
sp_comm <- na.omit(match(colnames(MD_pa_orig), colnames(JA_pa_orig)))
length(sp_comm)
colnames(JA_pa_orig)[sp_comm]
```
\  
\  
\  
\  
\  
\  
\  
\  



### Means, maximum and minimum of predictor variables
\  

#### Intermediate Extent
\  
DRF
```{r}
data.frame(DRF_min = apply(DRF_clim, 2, min), DRF_mean = apply(DRF_clim, 2, mean), DRF_max = apply(DRF_clim, 2, max))
data.frame(DRF_min = apply(DRF_env, 2, min), DRF_mean = apply(DRF_env, 2, mean), DRF_max = apply(DRF_env, 2, max))
```
\  

SSF
```{r}
data.frame(SSF_min = apply(SSF_clim, 2, min), SSF_mean = apply(SSF_clim, 2, mean), SSF_max = apply(SSF_clim, 2, max))
data.frame(SSF_min = apply(SSF_env, 2, min), SSF_mean = apply(SSF_env, 2, mean), SSF_max = apply(SSF_env, 2, max))

```


\  
\  


#### Small Extent

Ubatuba
```{r}
data.frame(UBA_min = apply(UBA_env, 2, min),
  UBA_mean = apply(UBA_env, 2, mean),
  UBA_max = apply(UBA_env, 2, max))
```
\  

Bertioga
```{r}
data.frame(BER_min = apply(BER_env, 2, min),
  BER_mean = apply(BER_env, 2, mean),
  BER_max = apply(BER_env, 2, max))
```
\  

Itanhaém
```{r}
data.frame(ITA_min = apply(ITA_env, 2, min),
  ITA_mean = apply(ITA_env, 2, mean),
  ITA_max = apply(ITA_env, 2, max))
```
\  

Santa Fé do Sul
```{r}
data.frame(ST_min = apply(ST_env, 2, min),
  ST_mean = apply(ST_env, 2, mean),
  ST_max = apply(ST_env, 2, max))
```
\  

Icém
```{r}
data.frame(IC_min = apply(IC_env, 2, min),
  IC_mean = apply(IC_env, 2, mean),
  IC_max = apply(IC_env, 2, max))
```
\  

Nova Itapirema
```{r}
data.frame(NI_min = apply(NI_env, 2, min),
  NI_mean = apply(NI_env, 2, mean),
  NI_max = apply(NI_env, 2, max))
```
\  


```{r}
data.frame(MD_min = apply(MD_env, 2, min),
  MD_mean = apply(MD_env, 2, mean),
  MD_max = apply(MD_env, 2, max))
```
\  

```{r}
data.frame(JA_min = apply(JA_env, 2, min),
  JA_mean = apply(JA_env, 2, mean),
  JA_max = apply(JA_env, 2, max))
```

\  
\  
\  
\  



### Coefficient of Variation of predictor variables

Intermediate Extent
```{r}
Int_Clim_cv <- data.frame(DRF_cv = apply(DRF_clim, 2, coef_var), SSF_cv = apply(SSF_clim, 2, coef_var))
Int_Env_cv <- data.frame(DRF_cv = apply(DRF_env, 2, coef_var), SSF_cv = apply(SSF_env, 2, coef_var))

Int_Clim_cv
Int_Env_cv

apply(Int_Clim_cv, 2, mean)
apply(Int_Env_cv, 2, mean)
```
\  
\  


Small Extent
```{r}
Sm_Env_cv <- data.frame(UBA_cv = apply(UBA_env, 2, coef_var),
           BER_cv = apply(BER_env, 2, coef_var),
           ITA_cv = apply(ITA_env, 2, coef_var),
           ST_cv = apply(ST_env, 2, coef_var),
           IC_cv = apply(IC_env, 2, coef_var),
           NI_cv = apply(NI_env, 2, coef_var),
           MD_cv = apply(MD_env, 2, coef_var),
           JA_cv = apply(JA_env, 2, coef_var))

Sm_Env_cv
apply(Sm_Env_cv, 2, mean)
```

