---
title: "Variation Partitioning"
author: "Rodolfo Pelinson"
date: "07/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


First we have to load the separated data matrices we need. The data matrices are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
source("Loading_data.R")
library(AtlanticForestMetacommunity)
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
library(AtlanticForestMetacommunity)
```

The used packages to run this analysis are:

`vegan` version 2.5-6   
`ade4` version 1.7-15   
`adespatial` version 0.3-8   

Some packages used to generate plots and tables

`dplyr` version 0.8.5   
`plotrix` version 3.7-8   

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(ade4)
library(adespatial)
library(dplyr)
library(plotrix)
```
\  
\  
\  
\  

## Reducing Multicolinearity

To remove multicolinear variables from our Environmental Matrix I built a function that removes variables with the variance inflation factor (VIF) higher than 3. The function `VIF_selection()` simply uses the `vif.cca()` from the `vegan` package. 
```{r}
Broad_env_VIF <- VIF_selection(Broad_pa,  Broad_env_st[,-6])

SSF_env_VIF <- VIF_selection(SSF_pa,  SSF_env_st)
ST_env_VIF <- VIF_selection(ST_pa,  ST_env_st)
IC_env_VIF <- VIF_selection(IC_pa,  IC_env_st)
NI_env_VIF <- VIF_selection(NI_pa,  NI_env_st)
MD_env_VIF <- VIF_selection(MD_pa,  MD_env_st)
JA_env_VIF <- VIF_selection(JA_pa,  JA_env_st)

DRF_env_VIF <- VIF_selection(DRF_pa,  DRF_env_st)
UBA_env_VIF <- VIF_selection(UBA_pa,  UBA_env_st)
BER_env_VIF <- VIF_selection(BER_pa,  BER_env_st)
ITA_env_VIF <- VIF_selection(ITA_pa,  ITA_env_st)
```
\  
\  


Same thing for climate variables
```{r}
Broad_clim_VIF <- VIF_selection(Broad_pa,  Broad_clim_st[,-6])
SSF_clim_VIF <- VIF_selection(SSF_pa,  SSF_clim_st)
DRF_clim_VIF <- VIF_selection(DRF_pa,  DRF_clim_st)
```
\  
\  

## Spatial Variables

Constructing matrices of spatial filters
```{r}
Broad_dbMEM <- dbmem(dist(Broad_coord), silent = F, thresh = NULL)

SSF_dbMEM <- dbmem(dist(SSF_coord), silent = F, thresh = NULL)
ST_dbMEM <- dbmem(dist(ST_coord), silent = F, thresh = NULL)
IC_dbMEM <- dbmem(dist(IC_coord), silent = F, thresh = NULL)
NI_dbMEM <- dbmem(dist(NI_coord), silent = F, thresh = NULL)
MD_dbMEM <- dbmem(dist(MD_coord), silent = F, thresh = NULL)
JA_dbMEM <- dbmem(dist(JA_coord), silent = F, thresh = NULL)

DRF_dbMEM <- dbmem(dist(DRF_coord), silent = F, thresh = NULL)
UBA_dbMEM <- dbmem(dist(UBA_coord), silent = F, thresh = NULL)
BER_dbMEM <- dbmem(dist(BER_coord), silent = F, thresh = NULL)
ITA_dbMEM <- dbmem(dist(ITA_coord), silent = F, thresh = NULL)

```
\  
\  
\  
\  


## Forward Selection

Similarly to removing variables with VIF higher than 3, I built a function to select the most important variables, when they could significantly explain species occurrences. This function mostly rely on the function `fs()` from package `adespatial`. Forward selection is only performed when the whole predictor matrix can significantly explain (p < 0.05) the variation in species occurrences.


### Broad Spatial Extent
```{r, cache = TRUE, warning=FALSE}
Broad_env_FS <- forward_selection(Broad_pa, Broad_env_VIF)
Broad_clim_FS <- forward_selection(Broad_pa, Broad_clim_VIF)
Broad_dbMEM_FS <- forward_selection(Broad_pa, Broad_dbMEM)
```


<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(Broad_env_FS)
```

<span style="color: #CB4335;">Retained Climate Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(Broad_clim_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(Broad_dbMEM_FS)
```
\  
\  

### Intermediate Spatial Extent
#### DRF
```{r, cache = TRUE, warning=FALSE}
DRF_env_FS <- forward_selection(DRF_pa, DRF_env_VIF)
DRF_clim_FS <- forward_selection(DRF_pa, DRF_clim_VIF)
DRF_dbMEM_FS <- forward_selection(DRF_pa, DRF_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(DRF_env_FS)
```

<span style="color: #CB4335;">Retained Climate Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(DRF_clim_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(DRF_dbMEM_FS)
```
\  
\ 

#### SSF
```{r, cache = TRUE, warning=FALSE}
SSF_env_FS <- forward_selection(SSF_pa, SSF_env_VIF)
SSF_clim_FS <- forward_selection(SSF_pa, SSF_clim_VIF)
SSF_dbMEM_FS <- forward_selection(SSF_pa, SSF_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(SSF_env_FS)
```

<span style="color: #CB4335;">Retained Climate Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(SSF_clim_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(SSF_dbMEM_FS)
```
\  
\  


### Small Spatial Extent
#### DRF
Ubatuba
```{r, cache = TRUE, warning=FALSE}
UBA_env_FS <- forward_selection(UBA_pa, UBA_env_VIF)
UBA_dbMEM_FS <- forward_selection(UBA_pa, UBA_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(UBA_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(UBA_dbMEM_FS)
```
\  
\  

Bertioga
```{r, cache = TRUE, warning=FALSE}
BER_env_FS <- forward_selection(BER_pa, BER_env_VIF)
BER_dbMEM_FS <- forward_selection(BER_pa, BER_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(BER_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(BER_dbMEM_FS)
```
\  
\  

Itanhaém
```{r, cache = TRUE, warning=FALSE}
ITA_env_FS <- forward_selection(ITA_pa, ITA_env_VIF)
ITA_dbMEM_FS <- forward_selection(ITA_pa, ITA_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(ITA_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(ITA_dbMEM_FS)
```
\  
\  

#### SSF
Santa Fé do Sul
```{r, cache = TRUE, warning=FALSE}
ST_env_FS <- forward_selection(ST_pa, ST_env_VIF)
ST_dbMEM_FS <- forward_selection(ST_pa, ST_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(ST_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(ST_dbMEM_FS)
```
\  
\  


Icém
```{r, cache = TRUE, warning=FALSE}
IC_env_FS <- forward_selection(IC_pa, IC_env_VIF)
IC_dbMEM_FS <- forward_selection(IC_pa, IC_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(IC_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(IC_dbMEM_FS)
```
\  
\  

Nova Itapirema
```{r, cache = TRUE, warning=FALSE}
NI_env_FS <- forward_selection(NI_pa, NI_env_VIF)
NI_dbMEM_FS <- forward_selection(NI_pa, NI_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(NI_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(NI_dbMEM_FS)
```
\  
\  

Morro do Diabo
```{r, cache = TRUE, warning=FALSE}
MD_env_FS <- forward_selection(MD_pa, MD_env_VIF)
MD_dbMEM_FS <- forward_selection(MD_pa, MD_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(MD_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(MD_dbMEM_FS)
```
\  
\  

Jataí
```{r, cache = TRUE, warning=FALSE}
JA_env_FS <- forward_selection(JA_pa, JA_env_VIF)
JA_dbMEM_FS <- forward_selection(JA_pa, JA_dbMEM)
```

<span style="color: #D4AC0D;">Retained Environmental Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(JA_env_FS)
```

<span style="color: #3498DB;">Retained Spatial Variables</span>
```{r, cache = TRUE, warning=FALSE}
colnames(JA_dbMEM_FS)
```
\  
\  
\  
\  



We can plot the important spatial variables to better understand what spatial patterns they describe.

Large Scale MEM 1, 2, 3 and 4.
```{r, fig.width= 6, fig.height=6,out.width= 800, out.height=800 , fig.align='center', dpi = 200}
par(mfrow = c(2,2))
sr_value(Broad_coord, Broad_dbMEM_FS[,1], ylim = c(-24.49270,-20.17833), xlim = c(-52.64536, -44.51492), grid=F, csize = 0.8, clegend = 1, xax = 2, yax = 1, method = "bubble")
title(main = "LARGE SCALE MEM 1", line = 3, outer = F, adj = 1)

sr_value(Broad_coord, Broad_dbMEM_FS[,2], ylim = c(-24.49270,-20.17833), xlim = c(-52.64536, -44.51492), grid=F, csize = 0.8, clegend = 1, xax = 2, yax = 1, method = "bubble")
title(main = "LARGE SCALE MEM 2", line = 3, outer = F, adj = 1)

sr_value(Broad_coord, Broad_dbMEM_FS[,3], ylim = c(-24.49270,-20.17833), xlim = c(-52.64536, -44.51492), grid=F, csize = 0.8, clegend = 1, xax = 2, yax = 1, method = "bubble")
title(main = "LARGE SCALE MEM 3", line = 3, outer = F, adj = 1)

sr_value(Broad_coord, Broad_dbMEM_FS[,4], ylim = c(-24.49270,-20.17833), xlim = c(-52.64536, -44.51492), grid=F, csize = 0.8, clegend = 1, xax = 2, yax = 1, method = "bubble")
title(main = "LARGE SCALE MEM 4", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  



Intermediate Scale DRF MEM 1.
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
par(mfrow = c(1,1))
sr_value(DRF_coord, DRF_dbMEM_FS[,1], ylim = c(-24.59270,-23.33123), xlim = c(-47.61181, -44.61492), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "DRF MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  



Intermediate Scale SSF MEM 1.
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(SSF_coord, SSF_dbMEM_FS[,1], ylim = c(-22.61958,-20.17833), xlim = c(-52.54536, -47.52589), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "SSF MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  


Small Extent DRF - Ubatuba MEM 1
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(UBA_coord, UBA_dbMEM_FS[,1], ylim = c(-23.37694,-23.33123), xlim = c(-44.95004, -44.80492), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Ubatuba MEM 1", line = 3, outer = F, adj = 1)


```

\  
\  


Small Extent DRF - Bertioga MEM 1
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(BER_coord, BER_dbMEM_FS[,1], ylim = c(-23.76198,-23.71684), xlim = c(-45.94223, -45.73709), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Bertioga MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  


Small Extent DRF - Itanhaém MEM 1 and 2.
```{r, fig.height= 3,fig.width=6,out.width= 800, out.height=400 , fig.align='center', dpi = 200}
par(mfrow = c(1,2))

sr_value(ITA_coord, ITA_dbMEM_FS[,1], ylim = c(-24.6527,-24.1786), xlim = c(-47.31181, -46.89443), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Itanhaém MEM 1", line = 3, outer = F, adj = 1)


sr_value(ITA_coord, ITA_dbMEM_FS[,2], ylim = c(-24.6527,-24.1786), xlim = c(-47.31181, -46.89443), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Itanhaém MEM 2", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  



Small Extent DRF - Santa Fé do Sul MEM 1 and 2.
```{r, fig.height= 3,fig.width=6,out.width= 800, out.height=400 , fig.align='center', dpi = 200}
par(mfrow = c(1,2))

sr_value(ST_coord, ST_dbMEM_FS[,1], ylim = c(-20.18789,-20.17733), xlim = c(-50.89639, -50.89056), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Santa Fé do Sul MEM 1", line = 3, outer = F, adj = 1)


sr_value(ST_coord, ST_dbMEM_FS[,2], ylim = c(-20.18789,-20.17733), xlim = c(-50.89639, -50.89056), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Santa Fé do Sul MEM 2", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  



Small Extent DRF - Icém MEM 1 and 2.
```{r, fig.height= 3,fig.width=6,out.width= 800, out.height=400 , fig.align='center', dpi = 200}
par(mfrow = c(1,2))

sr_value(IC_coord, IC_dbMEM_FS[,1], ylim = c(-20.375,-20.355), xlim = c(-49.28556, -49.18333), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Icém MEM 1", line = 3, outer = F, adj = 1)


sr_value(IC_coord, IC_dbMEM_FS[,2], ylim = c(-20.375,-20.355), xlim = c(-49.28556, -49.18333), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Icém MEM 2", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  





Small Extent DRF - Nova Itapirema MEM 1.
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(NI_coord, NI_dbMEM_FS[,1], ylim = c(-21.08111,-21.07333), xlim = c(-49.54072, -49.51689), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Nova Itapirema MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  




Small Extent DRF - Morro do Diabo MEM 1.
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(MD_coord, MD_dbMEM_FS[,1], ylim = c(-22.65958, -22.34950), xlim = c(-52.34536, -52.16550), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Morro do Diabo MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  



Small Extent DRF - Jataí MEM 1.
```{r, fig.height= 3,fig.width=3,out.width= 400, out.height=400 , fig.align='center', dpi = 200}
sr_value(JA_coord, JA_dbMEM_FS[,1], ylim = c(-21.58556, -21.56376), xlim = c(-47.79086, -47.72289), grid=F, csize = 0.8, clegend = 0.8, xax = 2, yax = 1, method = "bubble")
title(main = "Jataí MEM 1", line = 3, outer = F, adj = 1)

```

\  
\  
\  
\  


## Variation Partitioning
 
 

#### Large Extent
```{r, cache = TRUE}
#Variation partitioning Broad
Broad_varpart <- var_partitioning_1(Y = Broad_pa, 
                                       env = Broad_env_FS,
                                       clim = Broad_clim_FS,
                                       spa = Broad_dbMEM_FS, percent_r2 = F)
Broad_varpart
```
\  
\  
 
#### Intermediate Extent
```{r, cache = TRUE}
DRF_varpart <- var_partitioning_1(Y = DRF_pa, 
                                      env = DRF_env_FS,
                                      clim = DRF_clim_FS,
                                      spa = DRF_dbMEM_FS, percent_r2 = F)

SSF_varpart <- var_partitioning_1(Y = SSF_pa, 
                                      env = SSF_env_FS,
                                      clim = SSF_clim_FS,
                                      spa = SSF_dbMEM_FS, percent_r2 = F)

SSF_varpart
DRF_varpart
```
\  
\  
 
#### Small Extent

Small Extent allowing negative fractions
```{r, cache = TRUE}
ST_varpart <- var_partitioning_2(ST_pa, ST_env_FS, ST_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
IC_varpart <- var_partitioning_2(IC_pa, IC_env_FS, IC_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
NI_varpart <- var_partitioning_2(NI_pa, NI_env_FS, NI_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
MD_varpart <- var_partitioning_2(MD_pa, MD_env_FS, MD_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
JA_varpart <- var_partitioning_2(JA_pa, JA_env_FS, JA_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)

UBA_varpart <- var_partitioning_2(UBA_pa, UBA_env_FS, UBA_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
BER_varpart <- var_partitioning_2(BER_pa, BER_env_FS, BER_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)
ITA_varpart <- var_partitioning_2(ITA_pa, ITA_env_FS, ITA_dbMEM_FS, allow_negative_r2 = T, percent_r2 = F)

ST_varpart
IC_varpart
NI_varpart
MD_varpart
JA_varpart

UBA_varpart
BER_varpart
ITA_varpart
```
\  
\  
  
  

Small Extent not allowing negative fractions
```{r, cache = TRUE}
ST_varpart2 <- var_partitioning_2(ST_pa, ST_env_FS, ST_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
IC_varpart2 <- var_partitioning_2(IC_pa, IC_env_FS, IC_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
NI_varpart2 <- var_partitioning_2(NI_pa, NI_env_FS, NI_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
MD_varpart2 <- var_partitioning_2(MD_pa, MD_env_FS, MD_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
JA_varpart2 <- var_partitioning_2(JA_pa, JA_env_FS, JA_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)

UBA_varpart2 <- var_partitioning_2(UBA_pa, UBA_env_FS, UBA_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
BER_varpart2 <- var_partitioning_2(BER_pa, BER_env_FS, BER_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)
ITA_varpart2 <- var_partitioning_2(ITA_pa, ITA_env_FS, ITA_dbMEM_FS, allow_negative_r2 = F, percent_r2 = F)

ST_varpart2
IC_varpart2
NI_varpart2
MD_varpart2
JA_varpart2

UBA_varpart2
BER_varpart2
ITA_varpart2
```
\  
\  

Constructing a matrix with all R2 values 
```{r, message=FALSE, warning=FALSE}

Varpart_plot <- full_join(data.frame(rbind(Broad_varpart[,1])),
                          data.frame(rbind(SSF_varpart[,1])),)

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(DRF_varpart[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(ST_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(IC_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(NI_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(MD_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(JA_varpart2[,1])))
                          
Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(UBA_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(BER_varpart2[,1])))

Varpart_plot <- full_join(Varpart_plot,
                          data.frame(rbind(ITA_varpart2[,1])))

rownames(Varpart_plot) <- c("Broad", "SSF", "DRF", "Santa Fé do Sul", "Icém", "Nova Itapirema", "Morro do Diabo", "Jataí", "Ubatuba", "Bertioga", "Itanhaém")

Varpart_barplot <- t(Varpart_plot)
Varpart_barplot
```
\  
\    
\  
\      
  

Plotting the Variation Partioning as barplots.
```{r, fig.height= 7,fig.width=8,out.width= 800, out.height=700 , fig.align='center', dpi = 200}
Varpart_barplot <- Varpart_barplot[-c(1:4),]


for(i in 1:dim(Varpart_barplot)[1]){
  for(j in 1:dim(Varpart_barplot)[2]){
    if(is.na(Varpart_barplot[i,j])){Varpart_barplot[i,j] <- 0}
  }
}


Varpart_barplot_break <- Varpart_barplot; Varpart_barplot_break[8,] <- Varpart_barplot_break[8,]-0.3

Varpart_barplot_break <- Varpart_barplot_break[c(1,4,3,6,2,5,7,8),]

barplot(as.matrix(Varpart_barplot_break), axes = F, col = c(Pure_Env = "gold",
                                                            Env_Spa = mix_color(alpha = 0.4,"gold","cornflowerblue"),
                                                            Pure_Spa = "cornflowerblue",
                                                            Spa_Clim  = mix_color(alpha = 0.4,"brown1","cornflowerblue"),
                                                            Pure_Clim = "brown1",
                                                            Env_Clim  = mix_color(alpha = 0.4,"brown1","gold"),
                                                            Spa_Clim_Env = mix_color(alpha = 0.7,"brown1","grey"),
                                                            Resid = "grey80"), space = c(0,2,1,2,1,1,1,1,2,1,1), border = "white",
        legend.text = c("Environment","Environment-Space","Space","Climate-Space","Climate","Climate-Environment","All three","Residual"), ylim = c(0,0.8),
        args.legend	= list(x = -0.5,y = 0.85, yjust = 1,xjust = 0, horiz = F, ncol = 4, box.col = "transparent",text.width = 5, border = "white"), axisnames= F, ylab = "Adjusted R²", cex.lab = 1.25)
axis(2, at = c(0,0.1,0.2,0.3,0.4,0.5,0.6, 0.7), labels = c("0 %","10 %","20 %","30 %","40 %","50 %","60 %","100 %"))
axis.break(2, 0.65, style = "slash") 
axis(1,at = c(0.5,4.5,16),line = 2, labels =c("Broad","Intermediate","Fine"), tick = F,las = 1, hadj = 0.5, cex.axis = 1.3)
axis(1,at = c(12.5,21.5),line = 0.5, labels =c("SSF","DRF"), tick = F,las = 1, hadj = 0.5, cex.axis = 1.1)
text(c(0.5,   3.5,5.5   ,8.5,10.5,12.5,14.5,16.5,    19.5,21.5,23.5),rep(0.69,11), labels =c("All","SSF","DRF","Santa Fé do Sul","Icém","Nova Itapirema","Morro do Diabo","Jataí","Ubatuba","Bertioga","Itanhaém"), srt = 90, adj = 1, col = "grey45")
text(c(8.5,14.5,16.5,21.5,23.5),c(0.045,0.07,0.54,0.01,0.05), labels =c("*","*","*","*","*"), adj = 0.5, col = "white", cex = 2)
text(c(0.5,0.5,0.5),c(0.02,0.07,0.205), labels =c("*","*","*"), adj = 0.5, col = "white", cex = 2)
text(c(3.5,3.5,5.5),c(0.04,0.155,0.035), labels =c("*","*","*"), adj = 0.5, col = "white", cex = 2)

```
The asterisks represent significant fractions.

\  
\    
\  
\      

To better understand what are the environmental variables that are important in each fraction, we looked at the RDA plots of environmental variables (local Environment and Climate) both unconstrained alone and constrained by spatial variables, that is, with and without the importance spatially structured variables.

Because here we are not looking at p or R2 values, we are not woried about multicolinearity or overfitting, so we are using all climate and environmental variables.

### Intermediate Extent

```{r, fig.height= 6,fig.width=12,out.width= 800, out.height=400 , fig.align='center', dpi = 200}
RDA_clim_SSF <- rda(SSF_pa, data.frame(SSF_clim_st, SSF_env_st))

species_scores_SSF <- scores(RDA_clim_SSF, display = c( "species"), scaling = 2, hill = T)
loadings_SSF <- 0.45*scores(RDA_clim_SSF, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_SSF) <- c("TS","RT","TP","PS","HYD","CC","ARE","DEP","VH")
col_SSF <- c("brown1","brown1","brown1","brown1","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_SSF <- as.matrix(dist(rbind(loadings_SSF,c(0,0))))[10,-10]
dists_SSF_prop <- dists_SSF/max(dists_SSF)

par(mfrow = c(1,2),mar = c(5, 5, 4, 2))
plot(RDA_clim_SSF, type="n", scaling = 2, xlim = c(-0.5,0.5), ylim = c(-0.5,0.5), cex.lab = 2, cex.axis = 1.5, main = "SSF - Unconstrained")
for(i in 1:length(species_scores_SSF[,1])){
  points(species_scores_SSF[i,1], species_scores_SSF[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_SSF[i,1], species_scores_SSF[i,2], labels = rownames(species_scores_SSF)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_SSF[,1])),
              y0 = rep(0, length(loadings_SSF[,1])),
              x1 = loadings_SSF[,1],
              y1 = loadings_SSF[,2], col = col_SSF, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_SSF[,1])){
  points(loadings_SSF[i,1], loadings_SSF[i,2], col = col_SSF[i], pch = 21, cex = ((7*dists_SSF_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_SSF[i,1], loadings_SSF[i,2], labels = rownames(loadings_SSF)[i],col = col_SSF[i], cex = (1.4*dists_SSF_prop[i]))
}




RDA_clim_SSF <- rda(SSF_pa, data.frame(SSF_clim_st, SSF_env_st), data.frame(SSF_dbMEM_FS))

species_scores_SSF <- scores(RDA_clim_SSF, display = c( "species"), scaling = 2, hill = T)
loadings_SSF <- 0.45*scores(RDA_clim_SSF, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_SSF) <- c("TS","RT","TP","PS","HYD","CC","ARE","DEP","VH")
col_SSF <- c("brown1","brown1","brown1","brown1","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_SSF <- as.matrix(dist(rbind(loadings_SSF,c(0,0))))[10,-10]
dists_SSF_prop <- dists_SSF/max(dists_SSF)


plot(RDA_clim_SSF, type="n", scaling = 2, xlim = c(-0.65,0.35), ylim = c(-0.65,0.35), cex.lab = 2, cex.axis = 1.5, main = "SSF - Constrained")
for(i in 1:length(species_scores_SSF[,1])){
  points(species_scores_SSF[i,1], species_scores_SSF[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_SSF[i,1], species_scores_SSF[i,2], labels = rownames(species_scores_SSF)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_SSF[,1])),
              y0 = rep(0, length(loadings_SSF[,1])),
              x1 = loadings_SSF[,1],
              y1 = loadings_SSF[,2], col = col_SSF, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_SSF[,1])){
  points(loadings_SSF[i,1], loadings_SSF[i,2], col = col_SSF[i], pch = 21, cex = ((7*dists_SSF_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_SSF[i,1], loadings_SSF[i,2], labels = rownames(loadings_SSF)[i],col = col_SSF[i], cex = (1.4*dists_SSF_prop[i]))
}
```



```{r, fig.height= 6,fig.width=12,out.width= 800, out.height=400 , fig.align='center', dpi = 200}
RDA_clim_DRF <- rda(DRF_pa, data.frame(DRF_clim_st,DRF_env_st))

species_scores_DRF <- scores(RDA_clim_DRF, display = c( "species"), scaling = 2, hill = T)
loadings_DRF <- 0.45*scores(RDA_clim_DRF, display = c( "bp"), scaling = 0, hill = T)


rownames(loadings_DRF) <- c("TS","RT","TP","PS","HYD","CC","ARE","DEP","VH")
col_DRF <- c("brown1","brown1","brown1","brown1","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")


dists_DRF <- as.matrix(dist(rbind(loadings_DRF,c(0,0))))[10,-10]
dists_DRF_prop <- dists_DRF/max(dists_DRF)


par(mfrow = c(1,2),mar = c(5, 5, 4, 2))
plot(RDA_clim_DRF, type="n", scaling = 2, xlim = c(-0.6,0.5), ylim = c(-0.5,0.5), cex.lab = 2, cex.axis = 1.5, main = "DRF - Unconstrained")
for(i in 1:length(species_scores_DRF[,1])){
  points(species_scores_DRF[i,1], species_scores_DRF[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_DRF[i,1], species_scores_DRF[i,2], labels = rownames(species_scores_DRF)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_DRF[,1])),
              y0 = rep(0, length(loadings_DRF[,1])),
              x1 = loadings_DRF[,1],
              y1 = loadings_DRF[,2], col = col_DRF, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_DRF[,1])){
  points(loadings_DRF[i,1], loadings_DRF[i,2], col = col_DRF[i], pch = 21, cex = ((7*dists_DRF_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_DRF[i,1], loadings_DRF[i,2], labels = rownames(loadings_DRF)[i],col = col_DRF[i], cex = (1.4*dists_DRF_prop[i]))
}



#########################RDA DRF Constrained
RDA_clim_DRF <- rda(DRF_pa, data.frame(DRF_clim_st,DRF_env_st), data.frame(DRF_dbMEM_FS))


species_scores_DRF <- scores(RDA_clim_DRF, display = c( "species"), scaling = 2, hill = T)
loadings_DRF <- 0.45*scores(RDA_clim_DRF, display = c( "bp"), scaling = 0, hill = T)


rownames(loadings_DRF) <- c("TS","RT","TP","PS","HYD","CC","ARE","DEP","VH")
col_DRF <- c("brown1","brown1","brown1","brown1","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_DRF <- as.matrix(dist(rbind(loadings_DRF,c(0,0))))[10,-10]
dists_DRF_prop <- dists_DRF/max(dists_DRF)


plot(RDA_clim_DRF, type="n", scaling = 2, xlim = c(-0.4,0.5), ylim = c(-0.4,0.4), cex.lab = 2, cex.axis = 1.5, main = "DRF - Constrained")
for(i in 1:length(species_scores_DRF[,1])){
  points(species_scores_DRF[i,1], species_scores_DRF[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_DRF[i,1], species_scores_DRF[i,2], labels = rownames(species_scores_DRF)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_DRF[,1])),
              y0 = rep(0, length(loadings_DRF[,1])),
              x1 = loadings_DRF[,1],
              y1 = loadings_DRF[,2], col = col_DRF, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_DRF[,1])){
  points(loadings_DRF[i,1], loadings_DRF[i,2], col = col_DRF[i], pch = 21, cex = ((7*dists_DRF_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_DRF[i,1], loadings_DRF[i,2], labels = rownames(loadings_DRF)[i],col = col_DRF[i], cex = (1.4*dists_DRF_prop[i]))
}

```

\  
\    
\  
\     


### Small Extent

Because there were no shared fractions between spatial and environmental variables at small spatial extent, we only plotted constrained ordinations.

#### SSF

```{r, fig.height= 6,fig.width=12,out.width= 800, out.height=400 , fig.align='center', dpi = 200, fig.show="hold"}
#SANTA FÈ DO SUL
RDA_clim_ST <- rda(ST_pa, data.frame(ST_env_st), data.frame(ST_dbMEM_FS))

species_scores_ST <- scores(RDA_clim_ST, display = c( "species"), scaling = 2, hill = T)
loadings_ST <- 0.45*scores(RDA_clim_ST, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_ST) <- c("HYD","ARE","DEP","VH")
col_ST <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_ST <- as.matrix(dist(rbind(loadings_ST,c(0,0))))[5,-5]
dists_ST_prop <- dists_ST/max(dists_ST)

par(mfrow = c(1,2),mar = c(5, 5, 4, 2))
plot(RDA_clim_ST, type="n", scaling = 2 , xlim = c(-0.6,0.6), ylim = c(-0.6,0.6), cex.lab = 2, cex.axis = 1.5, main = "Santa Fé do Sul")

for(i in 1:length(species_scores_ST[,1])){
  points(species_scores_ST[i,1], species_scores_ST[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_ST[i,1], species_scores_ST[i,2], labels = rownames(species_scores_ST)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_ST[,1])),
              y0 = rep(0, length(loadings_ST[,1])),
              x1 = loadings_ST[,1],
              y1 = loadings_ST[,2], col = col_ST, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_ST[,1])){
  points(loadings_ST[i,1], loadings_ST[i,2], col = col_ST[i], pch = 21, cex = ((7*dists_ST_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_ST[i,1], loadings_ST[i,2], labels = rownames(loadings_ST)[i],col = col_ST[i], cex = (1.4*dists_ST_prop[i]))
}

#ICÉM
RDA_clim_IC <- rda(IC_pa, data.frame(IC_env_st), data.frame(IC_dbMEM_FS))

species_scores_IC <- scores(RDA_clim_IC, display = c( "species"), scaling = 2, hill = T)
loadings_IC <- 0.45*scores(RDA_clim_IC, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_IC) <- c("HYD","ARE","DEP","VH")
col_IC <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_IC <- as.matrix(dist(rbind(loadings_IC,c(0,0))))[5,-5]
dists_IC_prop <- dists_IC/max(dists_IC)

plot(RDA_clim_IC, type="n", scaling = 2 , xlim = c(-0.6,0.6), ylim = c(-0.6,0.6), cex.lab = 2, cex.axis = 1.5, main = "Icém")
for(i in 1:length(species_scores_IC[,1])){
  points(species_scores_IC[i,1], species_scores_IC[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_IC[i,1], species_scores_IC[i,2], labels = rownames(species_scores_IC)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_IC[,1])),
              y0 = rep(0, length(loadings_IC[,1])),
              x1 = loadings_IC[,1],
              y1 = loadings_IC[,2], col = col_IC, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_IC[,1])){
  points(loadings_IC[i,1], loadings_IC[i,2], col = col_IC[i], pch = 21, cex = ((7*dists_IC_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_IC[i,1], loadings_IC[i,2], labels = rownames(loadings_IC)[i],col = col_IC[i], cex = (1.4*dists_IC_prop[i]))
}

#NOVA ITAPIREMA
RDA_clim_NI <- rda(NI_pa, data.frame(NI_env_st), data.frame(NI_dbMEM_FS))

species_scores_NI <- scores(RDA_clim_NI, display = c( "species"), scaling = 2, hill = T)
loadings_NI <- 0.45*scores(RDA_clim_NI, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_NI) <- c("HYD","ARE","DEP","VH")
col_NI <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_NI <- as.matrix(dist(rbind(loadings_NI,c(0,0))))[5,-5]
dists_NI_prop <- dists_NI/max(dists_NI)

plot(RDA_clim_NI, type="n", scaling = 2 , xlim = c(-0.6,0.6), ylim = c(-0.6,0.6), cex.lab = 2, cex.axis = 1.5, main = "Nova Itapirema")
for(i in 1:length(species_scores_NI[,1])){
  points(species_scores_NI[i,1], species_scores_NI[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_NI[i,1], species_scores_NI[i,2], labels = rownames(species_scores_NI)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_NI[,1])),
              y0 = rep(0, length(loadings_NI[,1])),
              x1 = loadings_NI[,1],
              y1 = loadings_NI[,2], col = col_NI, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_NI[,1])){
  points(loadings_NI[i,1], loadings_NI[i,2], col = col_NI[i], pch = 21, cex = ((7*dists_NI_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_NI[i,1], loadings_NI[i,2], labels = rownames(loadings_NI)[i],col = col_NI[i], cex = (1.4*dists_NI_prop[i]))
}


#MORRO DO DIABO
RDA_clim_MD <- rda(MD_pa, data.frame(MD_env_st), data.frame(MD_dbMEM_FS))

species_scores_MD <- scores(RDA_clim_MD, display = c( "species"), scaling = 2, hill = T)
loadings_MD <- 0.45*scores(RDA_clim_MD, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_MD) <- c("HYD","CC","ARE","DEP","VH")
col_MD <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_MD <- as.matrix(dist(rbind(loadings_MD,c(0,0))))[6,-6]
dists_MD_prop <- dists_MD/max(dists_MD)

plot(RDA_clim_MD, type="n", scaling = 2 , xlim = c(-0.5,0.6), ylim = c(-0.5,0.6), cex.lab = 2, cex.axis = 1.5, main = "Morro do Diabo")
for(i in 1:length(species_scores_MD[,1])){
  points(species_scores_MD[i,1], species_scores_MD[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_MD[i,1], species_scores_MD[i,2], labels = rownames(species_scores_MD)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_MD[,1])),
              y0 = rep(0, length(loadings_MD[,1])),
              x1 = loadings_MD[,1],
              y1 = loadings_MD[,2], col = col_MD, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_MD[,1])){
  points(loadings_MD[i,1], loadings_MD[i,2], col = col_MD[i], pch = 21, cex = ((7*dists_MD_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_MD[i,1], loadings_MD[i,2], labels = rownames(loadings_MD)[i],col = col_MD[i], cex = (1.4*dists_MD_prop[i]))
}

#JATAÍ
RDA_clim_JA <- rda(JA_pa, data.frame(JA_env_st), data.frame(JA_dbMEM_FS))

species_scores_JA <- scores(RDA_clim_JA, display = c( "species"), scaling = 2, hill = T)
loadings_JA <- 0.45*scores(RDA_clim_JA, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_JA) <- c("HYD","CC","ARE","DEP","VH")
col_JA <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_JA <- as.matrix(dist(rbind(loadings_JA,c(0,0))))[6,-6]
dists_JA_prop <- dists_JA/max(dists_JA)


plot(RDA_clim_JA, type="n", scaling = 2 , xlim = c(-0.5,0.6), ylim = c(-0.5,0.6), cex.lab = 2, cex.axis = 1.5, main = "Jataí")
for(i in 1:length(species_scores_JA[,1])){
  points(species_scores_JA[i,1], species_scores_JA[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_JA[i,1], species_scores_JA[i,2], labels = rownames(species_scores_JA)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_JA[,1])),
              y0 = rep(0, length(loadings_JA[,1])),
              x1 = loadings_JA[,1],
              y1 = loadings_JA[,2], col = col_JA, lwd = 2, arr.type="triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_JA[,1])){
  points(loadings_JA[i,1], loadings_JA[i,2], col = col_JA[i], pch = 21, cex = ((7*dists_JA_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_JA[i,1], loadings_JA[i,2], labels = rownames(loadings_JA)[i],col = col_JA[i], cex = (1.4*dists_JA_prop[i]))
}
```

\  
\    
\  
\     

#### DRF

```{r, fig.height= 6,fig.width=12,out.width= 800, out.height=400 , fig.align='center', dpi = 200, fig.show="hold"}
#UBATUBA
RDA_clim_UBA <- rda(UBA_pa, data.frame(UBA_env_st), data.frame(UBA_dbMEM_FS))

species_scores_UBA <- scores(RDA_clim_UBA, display = c( "species"), scaling = 2, hill = T)
loadings_UBA <- 0.45*scores(RDA_clim_UBA, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_UBA) <- c("HYD","CC","ARE","DEP")
col_UBA <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_UBA <- as.matrix(dist(rbind(loadings_UBA,c(0,0))))[5,-5]
dists_UBA_prop <- dists_UBA/max(dists_UBA)

par(mfrow = c(1,2),mar = c(5, 5, 4, 2))
plot(RDA_clim_UBA, type="n", scaling = 2 , xlim = c(-0.6,0.4), ylim = c(-0.5,0.4), cex.lab = 2, cex.axis = 1.5, main = "Ubatuba")
for(i in 1:length(species_scores_UBA[,1])){
  points(species_scores_UBA[i,1], species_scores_UBA[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_UBA[i,1], species_scores_UBA[i,2], labels = rownames(species_scores_UBA)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_UBA[,1])),
              y0 = rep(0, length(loadings_UBA[,1])),
              x1 = loadings_UBA[,1],
              y1 = loadings_UBA[,2], col = col_UBA, lwd = 2, arr.type= "triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_UBA[,1])){
  points(loadings_UBA[i,1], loadings_UBA[i,2], col = col_UBA[i], pch = 21, cex = ((7*dists_UBA_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_UBA[i,1], loadings_UBA[i,2], labels = rownames(loadings_UBA)[i],col = col_UBA[i], cex = (1.4*dists_UBA_prop[i]))
}

#BERTIOGA
RDA_clim_BER <- rda(BER_pa, data.frame(BER_env_st), data.frame(BER_dbMEM_FS))

species_scores_BER <- scores(RDA_clim_BER, display = c( "species"), scaling = 2, hill = T)
loadings_BER <- 0.45*scores(RDA_clim_BER, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_BER) <- c("HYD","CC","ARE","DEP")
col_BER <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_BER <- as.matrix(dist(rbind(loadings_BER,c(0,0))))[5,-5]
dists_BER_prop <- dists_BER/max(dists_BER)

plot(RDA_clim_BER, type="n", scaling = 2, xlim = c(-0.7,0.4), ylim = c(-0.3,0.4), cex.lab = 2, cex.axis = 1.5, main = "Bertioga")
for(i in 1:length(species_scores_BER[,1])){
  points(species_scores_BER[i,1], species_scores_BER[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_BER[i,1], species_scores_BER[i,2], labels = rownames(species_scores_BER)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_BER[,1])),
              y0 = rep(0, length(loadings_BER[,1])),
              x1 = loadings_BER[,1],
              y1 = loadings_BER[,2], col = col_BER, lwd = 2, arr.type= "triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_BER[,1])){
  points(loadings_BER[i,1], loadings_BER[i,2], col = col_BER[i], pch = 21, cex = ((7*dists_BER_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_BER[i,1], loadings_BER[i,2], labels = rownames(loadings_BER)[i],col = col_BER[i], cex = (1.4*dists_BER_prop[i]))
}

#ITANHAÉM
RDA_clim_ITA <- rda(ITA_pa, data.frame(ITA_env_st), data.frame(ITA_dbMEM_FS))

species_scores_ITA <- scores(RDA_clim_ITA, display = c( "species"), scaling = 2, hill = T)
loadings_ITA <- 0.45*scores(RDA_clim_ITA, display = c( "bp"), scaling = 0, hill = T)

rownames(loadings_ITA) <- c("HYD","CC","ARE","DEP","VH")
col_ITA <- c("darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod","darkgoldenrod")

dists_ITA <- as.matrix(dist(rbind(loadings_ITA,c(0,0))))[6,-6]
dists_ITA_prop <- dists_ITA/max(dists_ITA)

plot(RDA_clim_ITA, type="n", scaling = 2 , xlim = c(-0.7,0.4), ylim = c(-0.3,0.4), cex.lab = 2, cex.axis = 1.5, main = "Itanhaém")
for(i in 1:length(species_scores_ITA[,1])){
  points(species_scores_ITA[i,1], species_scores_ITA[i,2], col = "white", pch = 21, cex = 5, bg = "grey80", lwd = 1)
  text(species_scores_ITA[i,1], species_scores_ITA[i,2], labels = rownames(species_scores_ITA)[i],col = "black", cex = 0.8)
}

shape::Arrows(x0 = rep(0, length(loadings_ITA[,1])),
              y0 = rep(0, length(loadings_ITA[,1])),
              x1 = loadings_ITA[,1],
              y1 = loadings_ITA[,2], col = col_ITA, lwd = 2, arr.type= "triangle", arr.length = 0.1, arr.width = 0.1)

for(i in 1:length(loadings_ITA[,1])){
  points(loadings_ITA[i,1], loadings_ITA[i,2], col = col_ITA[i], pch = 21, cex = ((7*dists_ITA_prop[i])+1), bg = "white", lwd = 3)
  text(loadings_ITA[i,1], loadings_ITA[i,2], labels = rownames(loadings_ITA)[i],col = col_ITA[i], cex = (1.4*dists_ITA_prop[i]))
}
```

