---
title: "Variation Partitioning"
author: "Rodolfo Pelinson"
date: "07/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


First we have to load the separated data matrices we need. It all comes from the Data.csv file in the Data folder. The data matrices are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
library(AtlanticForestMetacommunity)
```

The used packages to run this analysis are:

`vegan` version 2.5-6
`ade4` version 1.7-15
`adespatial` version 0.3-8

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(ade4)
library(adespatial)
```



To remove multicolinear variables from our Environmental Matrix I built a function that removes variables with the variance inflation factor (VIF) higher than 3. The function `VIF_selection()` simply uses the `vif.cca()` from the `vegan` package. 
```{r}
Broad_env_VIF <- VIF_selection(Broad_pa,  Broad_env_st[,-6])

SSF_env_VIF <- VIF_selection(SSF_pa,  SSF_env_st)
ST_env_VIF <- VIF_selection(ST_pa,  ST_env_st)
IC_env_VIF <- VIF_selection(IC_pa,  IC_env_st)
NI_env_VIF <- VIF_selection(NI_pa,  NI_env_st)
MD_env_VIF <- VIF_selection(MD_pa,  MD_env_st)
JA_env_VIF <- VIF_selection(JA_pa,  JA_env_st)

DRF_env_VIF <- VIF_selection(DRF_pa,  DRF_env_st)
UBA_env_VIF <- VIF_selection(UBA_pa,  UBA_env_st)
BER_env_VIF <- VIF_selection(BER_pa,  BER_env_st)
ITA_env_VIF <- VIF_selection(ITA_pa,  ITA_env_st)
```


Same thing for climate variables
```{r}
Broad_clim_VIF <- VIF_selection(Broad_pa,  Broad_clim_st[,-6])
SSF_clim_VIF <- VIF_selection(SSF_pa,  SSF_clim_st)
DRF_clim_VIF <- VIF_selection(DRF_pa,  DRF_clim_st)
```


Constructing matrices of spatial filters
```{r}
Broad_dbMEM <- dbmem(dist(Broad_coord), silent = F, thresh = NULL)

SSF_dbMEM <- dbmem(dist(SSF_coord), silent = F, thresh = NULL)
ST_dbMEM <- dbmem(dist(ST_coord), silent = F, thresh = NULL)
IC_dbMEM <- dbmem(dist(IC_coord), silent = F, thresh = NULL)
NI_dbMEM <- dbmem(dist(NI_coord), silent = F, thresh = NULL)
MD_dbMEM <- dbmem(dist(MD_coord), silent = F, thresh = NULL)
JA_dbMEM <- dbmem(dist(JA_coord), silent = F, thresh = NULL)

DRF_dbMEM <- dbmem(dist(DRF_coord), silent = F, thresh = NULL)
UBA_dbMEM <- dbmem(dist(UBA_coord), silent = F, thresh = NULL)
BER_dbMEM <- dbmem(dist(BER_coord), silent = F, thresh = NULL)
ITA_dbMEM <- dbmem(dist(ITA_coord), silent = F, thresh = NULL)

```

