---
title: "Elements of Metacommunity Structure"
author: "Rodolfo Pelinson"
date: "12/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we need preparare all data matrices from the main dataset. These are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
library(AtlanticForestMetacommunity)
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
devtools::load_all()
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
```

The packages used to run this analyses are:

`vegan` version 2.5-6   
`metacom` version 1.5.3   


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(metacom)
library(scales)
```
\  
\  
\  
\  

Running the EMS analysis. The `IdentifyStructure` function is a function created to run the same analyses for multiple datasets and automatically identify the idealized metacommunity structure.
```{r, cache = TRUE, warning=FALSE, message=FALSE, comment=FALSE}
Metacommunities <- IdentifyStructure(list(Broad_pa,
                                          DRF_pa,#(Dense Rain Forest)
                                          UBA_pa,#(Ubatuba)
                                          BER_pa,#(Bertioga)
                                          ITA_pa,#(Itanhaém)
                                          SSF_pa,#(Seasonal Semideciduous Forest)
                                          ST_pa,#(Santa Fé do Sul)
                                          IC_pa,#(Icém)
                                          NI_pa,#(Nova Itapirema)
                                          MD_pa,#(Morro do Diabo)
                                          JA_pa),#(Estação Ecológica do Jataí)
                                     names = c("Broad",
                                               "DRF",
                                               "Ubatuba",
                                               "Bertioga",
                                               "Itanhaém",
                                               "SSF",
                                               "Santa Fé do Sul",
                                               "Icém",
                                               "Nova Itapirema",
                                               "Morro do Diabo",
                                               "Jataí"),
                                     CoherenceMethod = "curveball",
                                     turnoverMethod = "EMS",
                                     orderNulls = T, seed = 2, sims = 10000, round = 3)
Metacommunities
```
\ 
\ 


# Correlation with Environmental Gradients

We only analyzed the correlation between the underlying gradient with true environmental gradients for the metacommunities that exhibited a coherent metacommunity structures.
\  
\  

### Broad Spatial Extent

Spearman rank Correlations or Kruskal-Wallis analysis.
```{r, warning=FALSE, message=FALSE, cache=TRUE}
pca <- rda(Broad_clim_st)
relative_eigenvalues <- pca$CA$eig/sum(pca$CA$eig)
PC1 <- pca$CA$u[,1]
Broad_env$ecoregion <- as.factor(Broad_env$ecoregion)
Broad_spearman <- My_spearman(Broad_pa, data.frame(Broad_env, PC1))

round(Broad_spearman,3)
```
\  
\  

Plotting it.
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = Broad_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Clementsian Structure", xlab_line = 0.25, cex.xlab = 1.5,
           Env1 = PC1, Env.col_1 = c("white","red"), Env.label_1 = "Climate",
           Env2 = Broad_env_st$dist_to_forest, Env.col_2 = c("forestgreen","lemonchiffon"), Env.label_2 = "Dist. Forest",
           Env3 = as.numeric(Broad_env$nvt), Env.col_3 = c("lemonchiffon","forestgreen"), Env.label_3 = "Vegetation",
           Env4 = as.numeric(Broad_env$canopy_cover), Env.col_4= c("lemonchiffon","forestgreen"), Env.label_4 = "Canopy Cover",
           Env5 = as.numeric(Broad_env$ecoregion), Env.col_5= c("forestgreen","darkolivegreen2"), Env.label_5 = "Ecoregion")
```



### Intermediate Spatial Extent

#### DRF - Dense Rain Forest
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = DRF_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Dense Rain Forest", main_line = 3.5, cex.main = 1.25)
```


#### SSF - Seasonal Semideciduous Forest
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = SSF_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Seasonal Semideciduous Forest", main_line = 3.5, cex.main = 1.25)
```
\  
\  
\  
\  






### Intermediate Spatial Extent

#### DRF - Dense Rain Forest

Ubatuba
```{r, warning=FALSE, message=FALSE, cache=TRUE}
UBA_spearman <- My_spearman(UBA_pa, UBA_env)
round(UBA_spearman,3)

```


```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = UBA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Nested Structure: Clumped Species Loss", xlab_line = 0.25, cex.xlab = 1,
           main = "Ubatuba", main_line = 3.5, cex.main = 1.25)
```
\  
\  


Bertioga
```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = BER_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Bertioga", main_line = 3.5, cex.main = 1.25)
```

\  
\  


Itanhaém
```{r, warning=FALSE, message=FALSE, cache=TRUE}
ITA_spearman <- My_spearman(ITA_pa, ITA_env)
round(ITA_spearman,3)

```


```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = ITA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Nested Structure: Random Species Loss", xlab_line = 0.25, cex.xlab = 1,
           main = "Itanhaém", main_line = 3.5, cex.main = 1.25)
```

\  
\  


#### SSF - Seasonal Semideciduous Forest

Santa Fé do Sul
```{r, warning=FALSE, message=FALSE, cache=TRUE}
ST_spearman <- My_spearman(ST_pa, ST_env)
round(ST_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = ST_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Santa Fé do Sul", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Icém
```{r, warning=FALSE, message=FALSE, cache=TRUE}
IC_spearman <- My_spearman(IC_pa, IC_env)
round(IC_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = IC_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Icém", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Nova Itapirema
```{r, warning=FALSE, message=FALSE, cache=TRUE}
NI_spearman <- My_spearman(NI_pa, NI_env)
round(NI_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = NI_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Nova Itapirema", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Morro do Diabo
```{r, warning=FALSE, message=FALSE, cache=TRUE}
MD_spearman <- My_spearman(MD_pa, MD_env)
round(MD_spearman,3)
```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = MD_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Gleasonian Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Morro do Diabo", main_line = 3.5, cex.main = 1.25,
           Env1 = as.numeric(MD_env$canopy_cover), Env.col_1= c("lemonchiffon","forestgreen"), Env.label_1 = "Canopy Cover")
```
\  
\  

Jataí
```{r, warning=FALSE, message=FALSE, cache=TRUE}
JA_spearman <- My_spearman(JA_pa, JA_env)
round(JA_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = JA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Clementsian Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Jataí", main_line = 3.5, cex.main = 1.25,
           Env1 = as.numeric(JA_env$hydroperiod), Env.col_1 = c("lightskyblue", "royalblue"), Env.label_1 = "Hydroperiod",
           Env2 = as.numeric(JA_env$nvt), Env.col_2 = c("lemonchiffon","forestgreen"), Env.label_2 = "Vegetation",
           Env3 = as.numeric(JA_env$canopy_cover), Env.col_3 = c("lemonchiffon","forestgreen"), Env.label_3 = "Canopy Cover")
```
\  
\  
