---
title: "Elements of Metacommunity Structure"
author: "Rodolfo Pelinson"
date: "12/04/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we need preparare all data matrices from the main dataset. These are prepared sourcing the "Loading_data.R" file in the Auxiliary Scripts folder.
```{r, echo=TRUE, eval=FALSE}
library(AtlanticForestMetacommunity)
source("Loading_data.R")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
devtools::load_all()
source("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Auxiliary Scripts/Loading_data.R")
```

The packages used to run this analyses are:

`vegan` version 2.5-6   
`metacom` version 1.5.3   


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(metacom)
library(scales)
```
\  
\  
\  
\  

Running the EMS analysis. The `IdentifyStructure` function is a function created to run the same analyses for multiple datasets and automatically identify the idealized metacommunity structure.
```{r, cache = TRUE, warning=FALSE, message=FALSE, comment=FALSE}
Metacommunities <- IdentifyStructure(list(Broad_pa,
                                          DRF_pa,#(Dense Rain Forest)
                                          UBA_pa,#(Ubatuba)
                                          BER_pa,#(Bertioga)
                                          ITA_pa,#(Itanhaém)
                                          SSF_pa,#(Seasonal Semideciduous Forest)
                                          ST_pa,#(Santa Fé do Sul)
                                          IC_pa,#(Icém)
                                          NI_pa,#(Nova Itapirema)
                                          MD_pa,#(Morro do Diabo)
                                          JA_pa),#(Estação Ecológica do Jataí)
                                     names = c("Broad",
                                               "DRF",
                                               "Ubatuba",
                                               "Bertioga",
                                               "Itanhaém",
                                               "SSF",
                                               "Santa Fé do Sul",
                                               "Icém",
                                               "Nova Itapirema",
                                               "Morro do Diabo",
                                               "Jataí"),
                                     CoherenceMethod = "curveball",
                                     turnoverMethod = "EMS",
                                     orderNulls = T, seed = 2, sims = 10000, round = 3)
Metacommunities
```
\ 
\ 


# Correlation with Environmental Gradients

We only analyzed the correlation between the underlying gradient with true environmental gradients for the metacommunities that exhibited a coherent metacommunity structures.
\  
\  

### Broad Spatial Extent

Spearman rank Correlations or Kruskal-Wallis analysis.
```{r, warning=FALSE, message=FALSE, cache=TRUE}
pca <- rda(Broad_clim_st)
relative_eigenvalues <- pca$CA$eig/sum(pca$CA$eig)
PC1 <- pca$CA$u[,1]
Broad_env$ecoregion <- as.factor(Broad_env$ecoregion)
Broad_spearman <- My_spearman(Broad_pa, data.frame(Broad_env, PC1))

round(Broad_spearman,3)
```
\  
\  

Plotting it.
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = Broad_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Clementsian Structure", xlab_line = 0.25, cex.xlab = 1.5,
           Env1 = PC1, Env.col_1 = c("white","red"), Env.label_1 = "Climate",
           Env2 = Broad_env_st$dist_to_forest, Env.col_2 = c("forestgreen","lemonchiffon"), Env.label_2 = "Dist. Forest",
           Env3 = as.numeric(Broad_env$nvt), Env.col_3 = c("lemonchiffon","forestgreen"), Env.label_3 = "Vegetation",
           Env4 = as.numeric(Broad_env$canopy_cover), Env.col_4= c("lemonchiffon","forestgreen"), Env.label_4 = "Canopy Cover",
           Env5 = as.numeric(Broad_env$ecoregion), Env.col_5= c("forestgreen","darkolivegreen2"), Env.label_5 = "Ecoregion")
```



### Intermediate Spatial Extent

#### DRF - Dense Rain Forest
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = DRF_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Dense Rain Forest", main_line = 3.5, cex.main = 1.25)
```


#### SSF - Seasonal Semideciduous Forest
```{r, fig.height= 7,fig.width=10,out.width= 1000, out.height=700 , fig.align='center', dpi = 200}
My_Imagine(comm = SSF_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Seasonal Semideciduous Forest", main_line = 3.5, cex.main = 1.25)
```
\  
\  
\  
\  






### Intermediate Spatial Extent

#### DRF - Dense Rain Forest

Ubatuba
```{r, warning=FALSE, message=FALSE, cache=TRUE}
UBA_spearman <- My_spearman(UBA_pa, UBA_env)
round(UBA_spearman,3)

```


```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = UBA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Nested Structure: Clumped Species Loss", xlab_line = 0.25, cex.xlab = 1,
           main = "Ubatuba", main_line = 3.5, cex.main = 1.25)
```
\  
\  


Bertioga
```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = BER_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Bertioga", main_line = 3.5, cex.main = 1.25)
```

\  
\  


Itanhaém
```{r, warning=FALSE, message=FALSE, cache=TRUE}
ITA_spearman <- My_spearman(ITA_pa, ITA_env)
round(ITA_spearman,3)

```


```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = ITA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Nested Structure: Random Species Loss", xlab_line = 0.25, cex.xlab = 1,
           main = "Itanhaém", main_line = 3.5, cex.main = 1.25)
```

\  
\  


#### SSF - Seasonal Semideciduous Forest

Santa Fé do Sul
```{r, warning=FALSE, message=FALSE, cache=TRUE}
ST_spearman <- My_spearman(ST_pa, ST_env)
round(ST_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = ST_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Santa Fé do Sul", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Icém
```{r, warning=FALSE, message=FALSE, cache=TRUE}
IC_spearman <- My_spearman(IC_pa, IC_env)
round(IC_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = IC_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Icém", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Nova Itapirema
```{r, warning=FALSE, message=FALSE, cache=TRUE}
NI_spearman <- My_spearman(NI_pa, NI_env)
round(NI_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = NI_pa, col = c("white", "black"),
           order = T, scores = 1, fill = F, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Random Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Nova Itapirema", main_line = 3.5, cex.main = 1.25)
```
\  
\  

Morro do Diabo
```{r, warning=FALSE, message=FALSE, cache=TRUE}
MD_spearman <- My_spearman(MD_pa, MD_env)
round(MD_spearman,3)
```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = MD_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Gleasonian Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Morro do Diabo", main_line = 3.5, cex.main = 1.25,
           Env1 = as.numeric(MD_env$canopy_cover), Env.col_1= c("lemonchiffon","forestgreen"), Env.label_1 = "Canopy Cover")
```
\  
\  

Jataí
```{r, warning=FALSE, message=FALSE, cache=TRUE}
JA_spearman <- My_spearman(JA_pa, JA_env)
round(JA_spearman,3)

```

```{r, fig.height= 5,fig.width=6,out.width= 600, out.height=500 , fig.align='center', dpi = 200}
My_Imagine(comm = JA_pa, col = c("white", "black", "grey50"),
           order = T, scores = 1, fill = T, cex.site = 0.6, cex.species = 0.8, cex.envlab = 0.9,
           top_margin = 5, left_margin = 1.25, sitenames = FALSE, bottom_margin = 1.25, right_margin = 0.25, xline = -0.75,
           ylab = "Sites", ylab_line = 0, cex.ylab = 1.5, xlab = "Quasi-Clementsian Structure", xlab_line = 0.25, cex.xlab = 1,
           main = "Jataí", main_line = 3.5, cex.main = 1.25,
           Env1 = as.numeric(JA_env$hydroperiod), Env.col_1 = c("lightskyblue", "royalblue"), Env.label_1 = "Hydroperiod",
           Env2 = as.numeric(JA_env$nvt), Env.col_2 = c("lemonchiffon","forestgreen"), Env.label_2 = "Vegetation",
           Env3 = as.numeric(JA_env$canopy_cover), Env.col_3 = c("lemonchiffon","forestgreen"), Env.label_3 = "Canopy Cover")
```
\  
\  
\ 
\ 



# Exploring multiple sample sizes

We clearly have very different sample sizes among scales. 96 on the Broad scale, 46 and 50 on the intermediate one, and from 8 to 23 on the smallest ones. The number of communities in each scale clearly affects our ability to detect true co-occurrence patterns. Therefore, we repeated our analysis for the intermediate and large scale varying the number of observed communities to have a better idea of the validity of our results for the intermediate and small scales.
\ 
\ 


## Large scale with N = 50

```{r, echo=FALSE, eval = TRUE}
load("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Not Commit/Dados_EMS_subsampling_50.RData")
```

We got Random structures at the intermediate scales with an N ~ 50, and a Clementsian structure at the large scale with an N ~ 100. Lets see if we would get a similar result at large scale with an N = 50. 

To do so we sampled 50 communities from a total of 96 for 1000 times and calculated the metacommunity structure. To keep the a good representation of spatial scale we restricted our sampling procedure following:

 - 5 communities from each of the 5 areas of the SSF for a total of 25 communities from the SSF ecoregion.
 - 8 communities from each of the 3 areas of the DRF plus 1 community from any of those areas for a total of 25 communities from the DRF ecoregion.

```{r, eval = FALSE}
set.seed(3)
Broad_matrices_pa_50 <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
DRF_locality_levels <-levels(as.factor(DRF_locality))
id_SSF <- list()
id_DRF <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id_SSF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == SSF_locality_levels[i],]),5))
  }
  ids_SSF <- unlist(id_SSF)

  for(i in 1:length(DRF_locality_levels)){
    id_DRF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == DRF_locality_levels[i],]),8))
  }
  ids_DRF <- unlist(id_DRF)
  ids_DRF <- c(ids_DRF, sample(rownames(DRF_pa)[rownames(DRF_pa) %in% id_DRF == FALSE],1))
  ids <- c(ids_SSF,ids_DRF)
  oc_matrix <- Broad_pa[match(ids, rownames(Broad_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  Broad_matrices_pa_50[[j]] <- oc_matrix
}


Metacommunities_Broad_50 <- IdentifyStructure2(Broad_matrices_pa_50,
                                              CoherenceMethod = "curveball",
                                              turnoverMethod = "EMS",
                                              orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```

\ 

This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_Broad_50$p_Coherence[Metacommunities_Broad_50$p_Coherence < 0.05]) / length(Metacommunities_Broad_50$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 96 communities.
```{r}

names_structures <- c("Clementsian",
  "Quasi-Clementsian",
  "Gleasonian",
  "Quasi-Gleasonian",
  "Evenly-Spaced",
  "Quasi-Evenly-Spaced",
  "Nested with clumped species loss",
  "Quasi-Nested with clumped species loss",
  "Nested with random species loss",
  "Quasi-Nested with random species loss",
  "Nested with hyperdispersed species loss",
  "Quasi-Nested with hyperdispersed species loss",
  "Random")

Structures_50 <- c(rep(NA, 13))
names(Structures_50) <- names_structures

prop_Structures <- table(Metacommunities_Broad_50$Structure) / sum(table(Metacommunities_Broad_50$Structure)) 
Structures_50[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_50[is.na(Structures_50)] <- 0
Structures_50 <- Structures_50*100


Structures_50 <- as.matrix(t(data.frame(Structures = Structures_50[c(1,3,5,7,9,11,13)], Quasi = c(Structures_50[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_50,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "N = 50", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_50[,1],5), y = 0.5,labels = "*", cex = 2)
box()


```

Light grey bars are Quasi structures.
\ 

It seems that a sample size of 50 would be more than enough to identify the true co-occurrence pattern.
\ 
\ 










## Large and intermediate scales with N = 20

```{r, echo=FALSE}
load("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Not Commit/Dados_EMS_subsampling_20.RData")
```

Now lets see if we would get a similar results for the large and intermediate scales with an N = 20. 

### Intermediate Scale

#### SSF
We sampled 20 communities from a total of 46 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 4 communities from each of the 5 areas of the SSF for a total of 20 communities.

```{r, eval = FALSE}
SSF_matrices_pa_20 <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
id <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id[[i]] <- c(sample(rownames(SSF_pa[SSF_locality == SSF_locality_levels[i],]),4))
  }
  ids <- unlist(id)
  oc_matrix <- SSF_pa[match(ids, rownames(SSF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  SSF_matrices_pa_20[[j]] <- oc_matrix
}

Metacommunities_SSF_20 <- IdentifyStructure2(SSF_matrices_pa_20,
                                            CoherenceMethod = "curveball",
                                            turnoverMethod = "EMS",
                                            orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_SSF_20$p_Coherence[Metacommunities_SSF_20$p_Coherence < 0.05]) / length(Metacommunities_SSF_20$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_SSF_20 <- c(rep(NA, 13))
names(Structures_SSF_20) <- names_structures

prop_Structures <- table(Metacommunities_SSF_20$Structure) / sum(table(Metacommunities_SSF_20$Structure)) 
Structures_SSF_20[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_SSF_20[is.na(Structures_SSF_20)] <- 0
Structures_SSF_20 <- Structures_SSF_20*100


Structures_SSF_20 <- as.matrix(t(data.frame(Structures = Structures_SSF_20[c(1,3,5,7,9,11,13)], Quasi = c(Structures_SSF_20[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_SSF_20,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "SSF, N = 20", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_SSF_20[,7],5), y = 9.5,labels = "*", cex = 2)
box()

```

Light grey bars are Quasi structures.

\ 

#### DRF
We sampled 20 communities from a total of 50 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 7 communities from each of the 3 areas of the DRF, minus one of any of the selected communities for a total of 20 communities.

```{r, eval = FALSE}
DRF_matrices_pa_20 <- list()
DRF_locality_levels <-levels(as.factor(DRF_locality))
id <- list()

for(j in 1:1000){
  for(i in 1:length(DRF_locality_levels)){
    id[[i]] <- c(sample(rownames(DRF_pa[DRF_locality == DRF_locality_levels[i],]),7))
  }
  ids <- unlist(id)
  ids <- ids[-sample(ids,1)]
  oc_matrix <- DRF_pa[match(ids, rownames(DRF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  DRF_matrices_pa_20[[j]] <- oc_matrix
}

Metacommunities_DRF_20 <- IdentifyStructure2(DRF_matrices_pa_20,
                                            CoherenceMethod = "curveball",
                                            turnoverMethod = "EMS",
                                            orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_DRF_20$p_Coherence[Metacommunities_DRF_20$p_Coherence < 0.05]) / length(Metacommunities_DRF_20$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_DRF_20 <- c(rep(NA, 13))
names(Structures_DRF_20) <- names_structures

prop_Structures <- table(Metacommunities_DRF_20$Structure) / sum(table(Metacommunities_DRF_20$Structure)) 
Structures_DRF_20[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_DRF_20[is.na(Structures_DRF_20)] <- 0
Structures_DRF_20 <- Structures_DRF_20*100


Structures_DRF_20 <- as.matrix(t(data.frame(Structures = Structures_DRF_20[c(1,3,5,7,9,11,13)], Quasi = c(Structures_DRF_20[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_DRF_20,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "DRF, N = 20", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_DRF_20[,7],5), y = 9.5,labels = "*", cex = 2)

box()

```

Light grey bars are Quasi structures.

\ 



### Large scale with N = 20

We sampled 20 communities from a total of 96 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 2 communities from each of the 5 areas of the SSF for a total of 10 communities from the SSF ecoregion.
 - 3 communities from each of the 3 areas of the DRF plus 1 community from any of those areas for a total of 10 communities from the DRF ecoregion.

```{r, eval = FALSE}
set.seed(3)
Broad_matrices_pa_20 <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
DRF_locality_levels <-levels(as.factor(DRF_locality))
id_SSF <- list()
id_DRF <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id_SSF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == SSF_locality_levels[i],]),2))
  }
  ids_SSF <- unlist(id_SSF)

  for(i in 1:length(DRF_locality_levels)){
    id_DRF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == DRF_locality_levels[i],]),3))
  }
  ids_DRF <- unlist(id_DRF)
  ids_DRF <- c(ids_DRF, sample(rownames(DRF_pa)[rownames(DRF_pa) %in% id_DRF == FALSE],1))
  ids <- c(ids_SSF,ids_DRF)
  oc_matrix <- Broad_pa[match(ids, rownames(Broad_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  Broad_matrices_pa_20[[j]] <- oc_matrix
}


Metacommunities_Broad_20 <- IdentifyStructure2(Broad_matrices_pa_20,
                                              CoherenceMethod = "curveball",
                                              turnoverMethod = "EMS",
                                              orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_Broad_20$p_Coherence[Metacommunities_Broad_20$p_Coherence < 0.05]) / length(Metacommunities_Broad_20$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 96 communities.
```{r}

Structures_Broad_20 <- c(rep(NA, 13))
names(Structures_Broad_20) <- names_structures

prop_Structures <- table(Metacommunities_Broad_20$Structure) / sum(table(Metacommunities_Broad_20$Structure)) 
Structures_Broad_20[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_Broad_20[is.na(Structures_Broad_20)] <- 0
Structures_Broad_20 <- Structures_Broad_20*100


Structures_Broad_20 <- as.matrix(t(data.frame(Structures = Structures_Broad_20[c(1,3,5,7,9,11,13)], Quasi = c(Structures_Broad_20[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_Broad_20,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "Large, N = 20", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_Broad_20[,1],5), y = 0.5,labels = "*", cex = 2)

box()

```

Light grey bars are Quasi structures.

\ 

It seems that a sample size of 20 gives a good idea of the true co-occurrence pattern.
\ 
\ 











## Large and intermediate scales with N = 15

```{r, echo=FALSE}
load("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Not Commit/Dados_EMS_subsampling_15.RData")
```


Now lets see if we would get a similar results for the large and intermediate scales with an N = 20. 

### Intermediate Scale

#### SSF
We sampled 15 communities from a total of 46 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 3 communities from each of the 5 areas of the SSF for a total of 15 communities.


```{r, eval = FALSE}
set.seed(3)
SSF_matrices_pa_15 <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
id <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id[[i]] <- c(sample(rownames(SSF_pa[SSF_locality == SSF_locality_levels[i],]),3))
  }
  ids <- unlist(id)
  oc_matrix <- SSF_pa[match(ids, rownames(SSF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  SSF_matrices_pa_15[[j]] <- oc_matrix
}

Metacommunities_SSF_15 <- IdentifyStructure2(SSF_matrices_pa_15,
                                         CoherenceMethod = "curveball",
                                         turnoverMethod = "EMS",
                                         orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_SSF_15$p_Coherence[Metacommunities_SSF_15$p_Coherence < 0.05 & Metacommunities_SSF_15$z_Coherence < 0]) / length(Metacommunities_SSF_15$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_SSF_15 <- c(rep(NA, 13))
names(Structures_SSF_15) <- names_structures

prop_Structures <- table(Metacommunities_SSF_15$Structure) / sum(table(Metacommunities_SSF_15$Structure)) 
Structures_SSF_15[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_SSF_15[is.na(Structures_SSF_15)] <- 0
Structures_SSF_15 <- Structures_SSF_15*100


Structures_SSF_15 <- as.matrix(t(data.frame(Structures = Structures_SSF_15[c(1,3,5,7,9,11,13)], Quasi = c(Structures_SSF_15[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_SSF_15,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "SSF, N = 15", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_SSF_15[,7],5), y = 9.5,labels = "*", cex = 2)

box()

```

Light grey bars are Quasi structures.

\ 

#### DRF
We sampled 15 communities from a total of 50 for 1500 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 5 communities from each of the 3 areas of the DRF, plus one from any of those areas for a total of 15 communities.

```{r, eval = FALSE}
set.seed(3)
DRF_matrices_pa_15 <- list()
DRF_locality_levels <-levels(as.factor(DRF_locality))
id <- list()

for(j in 1:1000){
  for(i in 1:length(DRF_locality_levels)){
    id[[i]] <- c(sample(rownames(DRF_pa[DRF_locality == DRF_locality_levels[i],]),5))
  }
  ids <- unlist(id)
  oc_matrix <- DRF_pa[match(ids, rownames(DRF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  DRF_matrices_pa_15[[j]] <- oc_matrix
}
nrow(DRF_matrices_pa_15[[10]])

Metacommunities_DRF_15 <- IdentifyStructure2(DRF_matrices_pa_15,
                                         CoherenceMethod = "curveball",
                                         turnoverMethod = "EMS",
                                         orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_DRF_15$p_Coherence[Metacommunities_DRF_15$p_Coherence < 0.05 & Metacommunities_DRF_15$z_Coherence < 0]) / length(Metacommunities_DRF_15$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_DRF_15 <- c(rep(NA, 13))
names(Structures_DRF_15) <- names_structures

prop_Structures <- table(Metacommunities_DRF_15$Structure) / sum(table(Metacommunities_DRF_15$Structure)) 
Structures_DRF_15[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_DRF_15[is.na(Structures_DRF_15)] <- 0
Structures_DRF_15 <- Structures_DRF_15*100


Structures_DRF_15 <- as.matrix(t(data.frame(Structures = Structures_DRF_15[c(1,3,5,7,9,11,13)], Quasi = c(Structures_DRF_15[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_DRF_15,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "DRF, N = 15", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_DRF_15[,7],5), y = 9.5,labels = "*", cex = 2)

box()

```

Light grey bars are Quasi structures.

\ 




### Large scale with N = 15

We sampled 15 communities from a total of 96 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 2 community from each of the 5 areas of the SSF minus 2 or 3 of those communities for a total of 7 or 8 communities from the SSF ecoregion.
 - 2 communities from each of the 3 areas of the DRF, plus 1 or 2 communities from any of those areas for a total of 7 or 8 communities from the DRF ecoregion.

```{r, eval = FALSE}
set.seed(3)
Broad_matrices_pa_15 <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
DRF_locality_levels <-levels(as.factor(DRF_locality))
id_SSF <- list()
id_DRF <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id_SSF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == SSF_locality_levels[i],]),2))
  }
  ids_SSF <- unlist(id_SSF)
  minus <- sample(c(2,3),1)
  ids_SSF<- ids_SSF[-sample(1:length(ids_SSF),minus)]


  for(i in 1:length(DRF_locality_levels)){
    id_DRF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == DRF_locality_levels[i],]),2))
  }
  ids_DRF <- unlist(id_DRF)
  ids_DRF <- c(ids_DRF, sample(rownames(DRF_pa)[rownames(DRF_pa) %in% id_DRF == FALSE],(minus-1) ) )
  ids <- c(ids_SSF,ids_DRF)
  oc_matrix <- Broad_pa[match(ids, rownames(Broad_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  Broad_matrices_pa_15[[j]] <- oc_matrix
}


Metacommunities_Broad_15 <- IdentifyStructure2(Broad_matrices_pa_15,
                                           CoherenceMethod = "curveball",
                                           turnoverMethod = "EMS",
                                           orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_Broad_15$p_Coherence[Metacommunities_Broad_15$p_Coherence < 0.05 & Metacommunities_Broad_15$z_Coherence < 0]) / length(Metacommunities_Broad_15$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 96 communities.
```{r}

Structures_Broad_15 <- c(rep(NA, 13))
names(Structures_Broad_15) <- names_structures

prop_Structures <- table(Metacommunities_Broad_15$Structure) / sum(table(Metacommunities_Broad_15$Structure)) 
Structures_Broad_15[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_Broad_15[is.na(Structures_Broad_15)] <- 0
Structures_Broad_15 <- Structures_Broad_15*100


Structures_Broad_15 <- as.matrix(t(data.frame(Structures = Structures_Broad_15[c(1,3,5,7,9,11,13)], Quasi = c(Structures_Broad_15[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_Broad_15,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "Large, N = 15", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_Broad_15[,1],5), y = 0.5,labels = "*", cex = 2)

box()


```

Light grey bars are Quasi structures.

\ 

It seems that a sample size of 15 would only capture co-occurrence patterns that are too strong.
\ 
\ 













## Large and intermediate scales with N = 10

```{r, echo=FALSE}
load("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/AtlanticForestMetacommunity/Not Commit/Dados_EMS_subsampling.RData")
```

Now lets see if we would get a similar results for the large and intermediate scales with an N = 20. 

### Intermediate Scale

#### SSF
We sampled 10 communities from a total of 46 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 2 communities from each of the 5 areas of the SSF for a total of 10 communities.

```{r, eval = FALSE}
SSF_matrices_pa <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
id <- list()

set.seed(3)
for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id[[i]] <- c(sample(rownames(SSF_pa[SSF_locality == SSF_locality_levels[i],]),2))
  }
  ids <- unlist(id)
  oc_matrix <- SSF_pa[match(ids, rownames(SSF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  SSF_matrices_pa[[j]] <- oc_matrix
}

Metacommunities_SSF <- IdentifyStructure2(SSF_matrices_pa,
                                     CoherenceMethod = "curveball",
                                     turnoverMethod = "EMS",
                                     orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_SSF$p_Coherence[Metacommunities_SSF$p_Coherence < 0.05 & Metacommunities_SSF$z_Coherence < 0]) / length(Metacommunities_SSF$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_SSF <- c(rep(NA, 13))
names(Structures_SSF) <- names_structures

prop_Structures <- table(Metacommunities_SSF$Structure) / sum(table(Metacommunities_SSF$Structure)) 
Structures_SSF[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_SSF[is.na(Structures_SSF)] <- 0
Structures_SSF <- Structures_SSF*100


Structures_SSF <- as.matrix(t(data.frame(Structures = Structures_SSF[c(1,3,5,7,9,11,13)], Quasi = c(Structures_SSF[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_SSF,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "SSF, N = 10", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_SSF[,7],5), y = 9.5,labels = "*", cex = 2)
box()

```

Light grey bars are Quasi structures.

\ 

#### DRF
We sampled 10 communities from a total of 50 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 3 communities from each of the 3 areas of the DRF, plus one from any of those areas for a total of 10 communities.

```{r, eval = FALSE}
DRF_matrices_pa <- list()
DRF_locality_levels <-levels(as.factor(DRF_locality))
id <- list()

set.seed(3)
for(j in 1:1000){
  for(i in 1:length(DRF_locality_levels)){
    id[[i]] <- c(sample(rownames(DRF_pa[DRF_locality == DRF_locality_levels[i],]),3))
  }
  ids <- unlist(id)
  ids <- c(ids, sample(rownames(DRF_pa)[rownames(DRF_pa) %in% ids == FALSE],1))
  oc_matrix <- DRF_pa[match(ids, rownames(DRF_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  DRF_matrices_pa[[j]] <- oc_matrix
}

Metacommunities_DRF <- IdentifyStructure2(DRF_matrices_pa,
                                         CoherenceMethod = "curveball",
                                         turnoverMethod = "EMS",
                                         orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```
 


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_DRF$p_Coherence[Metacommunities_DRF$p_Coherence < 0.05 & Metacommunities_DRF$z_Coherence < 0]) / length(Metacommunities_DRF$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 46 communities.
```{r}

Structures_DRF <- c(rep(NA, 13))
names(Structures_DRF) <- names_structures

prop_Structures <- table(Metacommunities_DRF$Structure) / sum(table(Metacommunities_DRF$Structure)) 
Structures_DRF[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_DRF[is.na(Structures_DRF)] <- 0
Structures_DRF <- Structures_DRF*100


Structures_DRF <- as.matrix(t(data.frame(Structures = Structures_DRF[c(1,3,5,7,9,11,13)], Quasi = c(Structures_DRF[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_DRF,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "DRF, N = 10", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_DRF[,7],5), y = 9.5,labels = "*", cex = 2)
box()

```

Light grey bars are Quasi structures.

\ 



### Large scale with N = 10

We sampled 10 communities from a total of 96 for 1000 times and calculated the Metacommunity Structure (i.e. co-occurrence pattern). To keep a good representation of spatial scale we restricted our sampling procedure following:

 - 1 community from each of the 5 areas of the SSF for a total of 5 communities from the SSF ecoregion.
 - 2 communities from each of the 3 areas of the DRF, minus 1 community from any of those areas for a total of 5 communities from the DRF ecoregion.

```{r, eval = FALSE}
set.seed(3)
Broad_matrices_pa <- list()
SSF_locality_levels <-levels(as.factor(SSF_locality))
DRF_locality_levels <-levels(as.factor(DRF_locality))
id_SSF <- list()
id_DRF <- list()

for(j in 1:1000){
  for(i in 1:length(SSF_locality_levels)){
    id_SSF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == SSF_locality_levels[i],]),1))
  }
  ids_SSF <- unlist(id_SSF)

  for(i in 1:length(DRF_locality_levels)){
    id_DRF[[i]] <- c(sample(rownames(Broad_pa[Broad_locality == DRF_locality_levels[i],]),2))
  }
  ids_DRF <- unlist(id_DRF)
  ids_DRF <- ids_DRF[-sample(1:length(ids_DRF),1)]
  ids <- c(ids_SSF,ids_DRF)
  oc_matrix <- Broad_pa[match(ids, rownames(Broad_pa)),]
  oc_matrix <- oc_matrix[,colSums(oc_matrix) > 0]
  Broad_matrices_pa[[j]] <- oc_matrix
}


Metacommunities_Broad <- IdentifyStructure2(Broad_matrices_pa,
                                         CoherenceMethod = "curveball",
                                         turnoverMethod = "EMS",
                                         orderNulls = T, seed = 3, sims = 1000, round = 3, multicore = TRUE, n_cores = 10)
```


This is the percentage of coherent metacommunities found in our subsamples:
```{r}
length(Metacommunities_Broad_20$p_Coherence[Metacommunities_Broad_20$p_Coherence < 0.05]) / length(Metacommunities_Broad_20$p_Coherence)
```
\ 

These are the percentages of different structures identified. The asterisk indicate the Structure identified using all of the 96 communities.
```{r}

Structures_Broad <- c(rep(NA, 13))
names(Structures_Broad) <- names_structures

prop_Structures <- table(Metacommunities_Broad$Structure) / sum(table(Metacommunities_Broad$Structure)) 
Structures_Broad[match(names(prop_Structures), names_structures)] <- prop_Structures
Structures_Broad[is.na(Structures_Broad)] <- 0
Structures_Broad <- Structures_Broad*100


Structures_Broad <- as.matrix(t(data.frame(Structures = Structures_Broad[c(1,3,5,7,9,11,13)], Quasi = c(Structures_Broad[c(2,4,5,8,10,12)],0))))

par(mar = c(3.5,16,2,0.75), bty = "l")
barplot(Structures_Broad,
        axes = F, col = c("grey50", "grey80"), space = c(0, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
        border = "black", xlim = c(0,100), axisnames= F, xlab = "", cex.lab = 1.25, main = "Large, N = 10", horiz = TRUE, ylim = c(0,10))
title(xlab = "%", line = 2.5, cex.lab = 1.5)
axis(1)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = -0.25, labels =names_structures[c(1,3,5,7,9,11,13)], tick = F,las = 1, hadj = 1, cex.axis = 1, gap.axis = -1, padj = 0.4)
axis(2,at = c(0.5, 2, 3.5, 5, 6.5, 8, 9.5),line = 0, labels =FALSE, tick = T,las = 1, hadj = 1, cex.axis = 0.75, gap.axis = -1, padj = 0.4)
text(x = sum(Structures_Broad[,1],5), y = 0.5,labels = "*", cex = 2)
box()

```

Light grey bars are Quasi structures.

\ 

It seems that a sample size of 10 is not enough to capture the true structure. It seems to be able to capture coherence when it exists though.
\ 
\ 

